An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-04-25 Article/EconGrowth2.Rnw
moving to EconModels and EconData

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconModels2)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
require(plyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
require(knitr)

# Pull in some constants and other important functions
source("Scripts/files.R")
source(file.path("..", "Scripts", "Constants.R"))

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
# Adjust the levels of historicalData so that the levels are in the same order as countryAbbrevs.
for (lev in rev(countryAbbrevs)){
  historicalData$Country <- relevel(historicalData$Country, ref=lev)
}

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconModels)
require(EconData)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
require(plyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
require(knitr)

# Pull in some constants and other important functions
#source("Scripts/files.R")
#source(file.path("..", "Scripts", "Constants.R"))

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
historicalData <- Econ2011
